%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Sibi <sibi@psibi.in>
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tabularx}
\setlength\parskip{\baselineskip}
\begin{document}
\title{Automata : Week 1}
\author{Sibi}
\date{\today}
\maketitle
\newpage

\section{Introduction}

\begin{itemize}
  \item Automata is plural for automaton.
  \item Automatons are abstract models of machines that perform
    computations on an input by moving through a series of states or
    configurations. At each state of the computation, a transition
    function determines the next configuration on the basis of a
    finite portion of the present configuration.
\end{itemize}

\section{Finite Automata}

A finite automaton (FA) is a abstract machine used to recognize
patterns within input taken from some character set C. The job of the
FA is to accept or reject an input depending on whether the pattern
defined by the FA occurs in the input.

\begin{itemize}
\item It can be in exactly one of the finite number of states at a
  given time.
\item The set of strings accepted by an automaton A is the language of
  A. It's denoted by L(A).
\end{itemize}

\section{Terminology}

\subsection{Alphabet}

\begin{itemize}
\item A finite, non empty set of symbols.
\item Symbol : \(\Sigma\)
\end{itemize}

Examples:
\begin{itemize}
  \item \(\Sigma = \{0, 1\} \)
  \item \(\Sigma = \{a, b, ..., z\} \)
\end{itemize}

\subsection{Strings (or word)}

\begin{itemize}
\item A string is a finite sequence of symbols chosen from some alphabet.
\item Example: 0010 and 01 are strings from the alphabet $\Sigma = \{0,1\}$
\item Empty string is denoted by $\epsilon$
\item $\Sigma ^ * = $ set of all strings over alphabet $\Sigma$.
\item Length of the string is the number of positions for symbols in
  the string. Example 0110 has length 4.
\item Notation of length of string $w$ is $|w|$. Example: $|011| = 3$.
\end{itemize}

With the above terminolgy, we can redefine language. A language is a
subset of $\Sigma^*$ for some alphabet $\Sigma$.

\end{document}




